Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-16 paper.qmd
Updated Figure 17
Added handwritten digit 1 images with high error inside the non-linear cluster

#img_error_outside <- c(3554, 501, 4422, 6860, 3869, 1529, 4916, 6144)
img_error_outside <- c(501, 1529, 6144)

@@

@@

highd_error_2d_mnist + (imge_error_sample_outside / right_top_img / middle_img / right_bottom_img)
```

>>>>

#img_error_outside <- c(3554, 501, 4422, 6860, 3869, 1529, 4916, 6144)
#img_error_outside <- c(501, 1529, 6144)
img_error_outside <- c(999, 3650, 4916)

@@

##### inside
img_error_inside <- c(7228, 7363, 7650)

pixels_gathered_inside <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_error_inside)

imge_error_sample_inside <- pixels_gathered_inside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

highd_error_2d_mnist + (imge_error_sample_outside/ imge_error_sample_inside / right_top_img / middle_img / right_bottom_img)
```
